Fractional Types

### 2016-12-16 typespp.tex
small things

The syntactic category $\ft$ of fractional types introduces type expressions for iteration groupoids, symmetry groupoids, and their products. The combinators that relate these fractional types are in Fig.~\ref{pifrac:comb}. The bottom group includes identity and sequential composition $\circledcirc$ combinators and ensures that the combinators can be applied anywhere inside a product $\circledast$. There is also a combinator that relates two types $\order{c_1}$ and $\order{c_2}$ via $\order{\alpha}$ whenever $\alpha : c_1 \isotwo c_2$. Indeed if $c_1$ and $c_2$ are considered equivalent via a 2-combinator then we also consider their iteration groupoids to be equivalent. The top group ensures that $\circledast$ carries a symmetric monoidal structure with combinators witnessing the unit, commutativity, and associativity properties. The last two pairs combinators $\eta-/\epsilon-$ and $\eta+/\epsilon+$ are inspired from the definition of compact closed categories~\cite{ccc} which are
symmetric monoidal categories in which every object has a dual. They are the ones that witness the ``fractional'' nature of symmetry groupoids: they are indeed the multiplicative inverses of iteration groupoids.

>>>>

The syntactic category $\ft$ of fractional types introduces type expressions for iteration groupoids, symmetry groupoids, and their products. The combinators that relate these fractional types are in Fig.~\ref{pifrac:comb}. The bottom group includes identity and sequential composition~$\circledcirc$ combinators and ensures that the combinators can be applied anywhere inside a product $\circledast$. There is also a combinator that relates two types $\order{c_1}$ and $\order{c_2}$ via $\order{\alpha}$ whenever $\alpha : c_1 \isotwo c_2$. Indeed if $c_1$ and $c_2$ are considered equivalent via a 2-combinator then we also consider their iteration groupoids to be equivalent. The top group ensures that $\circledast$ carries a symmetric monoidal structure with combinators witnessing the unit, commutativity, and associativity properties. The last two pairs combinators $\eta-/\epsilon-$ and $\eta+/\epsilon+$ are inspired from the definition of compact closed categories~\cite{ccc} which are
symmetric monoidal categories in which every object has a dual. They are the ones that witness the ``fractional'' nature of symmetry groupoids: they are indeed the multiplicative inverses of iteration groupoids.
